\textit{Supplementary materials for}: Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2025-02-28 paper/supplement.tex
fixed supp fig 10 caption to match new order

    \caption{\textbf{Comparing LDA vs.~BERT embeddings.} The rows display the
    equivalents of main text Figure \slidingWindows C (top row), Figures 
    \questionCorrs A and \questionCorrs B (middle two rows), and Figure 
    \topicVariability B (bottom row) computed using LDA (left) and BERT 
    (right).}

>>>>

    \caption{\textbf{Comparing LDA vs.~BERT embeddings.} The rows display the
    equivalents of main text Figure \slidingWindows C (top row), Figure 
    \topicVariability B (second row), and Figures \questionCorrs A and 
    \questionCorrs B (bottom two rows) computed using LDA (left) and BERT 
    (right).}
